---
title: "parPerm for interaction effects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interaction effects using permutation testing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Simulation 2:
 - Three-group permutation test
 - n=120 (40 per group)
 - Number of voxels: 10 x 10 x 4
 - Significant area size: 2 x 2 x 1
 - Multiple comparison correction (p.adjust, method=BH)
 - Report false discovery rates. 
 - Factor 1: txt, Factor2: sex
 - Only interaction size of d=0.8
(e.g. generate 4 groups, 30 per groups, and only one group will have higher average)


```{r, include = FALSE}
library(tidyverse)
library(parPerm)
library(doParallel)
library(knitr)
library(oro.nifti)
```

```{r Create Dataset}
img.dim <- c(10,10,4)
n <- 120
set.seed(1)
voxel_data <- array(rnorm(prod(img.dim)*n),dim=c(img.dim,n))

#Create dataset with effect size (0, 0, 0.8)
voxel_data_set1 <- voxel_data
voxel_data_set1[4:5,4:5,3,91:120] <- voxel_data_set1[4:5,4:5,3,91:120] + 1.3

#Show the means have actually changed
lapply(1:90, function(x) mean(voxel_data_set1[4:5,4:5,3,x])) %>% unlist() %>% mean
lapply(91:120, function(x) mean(voxel_data_set1[4:5,4:5,3,x])) %>% unlist() %>% mean

#Create the nifti file
simulation_nifti <- nifti(voxel_data_set1, dim = c(10, 10, 4, 120))
#writeNIfTI(simulation_nifti, "simulation2_data")
```

```{r}
cov_mat_parperm <- cbind(rep(c(0,1),c(60,60)), rep(c(0,1,0,1),c(30,30,30,30)))

#Set1 -- where first column x = 0
xtx_1 <- xmat_trans(cov_mat_parperm[1:60,-1])
ymat_set1 <- ymat_trans(simulation_nifti)[,1:60]
cores <- detectCores()
cl <- makeCluster(cores[1]-1)
registerDoParallel(cl)

#miswrote the single column version
result_set1 <- run_permtest(x.mat = xtx_1, y = ymat_set1, columns = 1, split = 2, num_perms = 10000)

result_set1 %>% 
  as.data.frame()%>%
  mutate_if(is.numeric, function(x) p.adjust(p = x, method = "BH")) %>%
  arrange(V1) %>%
  head() %>% 
  kable()
```

```{r}
#Set2 -- where first column x = 1
xtx_2 <- xmat_trans(cov_mat_parperm[61:120,-1])
ymat_set2 <- ymat_trans(simulation_nifti)[,61:120]
cores <- detectCores()
cl <- makeCluster(cores[1]-1)
registerDoParallel(cl)

#miswrote the single column version
result_set2 <- run_permtest(x.mat = xtx_2, y = ymat_set2, columns = 1, split = 2, num_perms = 10000)

result_set2 %>% 
  as.data.frame()%>%
  mutate_if(is.numeric, function(x) p.adjust(p = x, method = "BH")) %>%
  arrange(V1) %>%
  head() %>% 
  kable()
```

Even parsing it out, doesn't quite seem to isolate the effect when effect size is 0.8. 

Suggesting if we up the effect size it might parse it out. Using 1.3 it starts to show. 


#Changing Effect Sizes
```{r, echo = FALSE}
#things to append/use iteratively
effect_size <- (5:15)/10
p_list <- vector("list")

#fixed things
img.dim <- c(10,10,4)
n <- 120
set.seed(1)
voxel_data <- array(rnorm(prod(img.dim)*n),dim=c(img.dim,n))
cov_mat_parperm <- cbind(rep(c(0,1),c(60,60)), rep(c(0,1,0,1),c(30,30,30,30)))
xtx <- xmat_trans(cov_mat_parperm[61:120,-1])

for(i in 1:length(effect_size)){
  voxel_data_set_i <- voxel_data
  voxel_data_set_i[4:5, 4:5, 2:3,91:120] <- voxel_data_set_i[4:5, 4:5, 2:3, 91:120] + effect_size[i]
  simulation_nifti <- nifti(voxel_data_set_i, dim = c(10, 10, 4, 120))
  ymat_set <- ymat_trans(simulation_nifti)[,61:120]
  cores <- detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
  
  #miswrote the single column version
  result_set <- run_permtest(x.mat = xtx, y = ymat_set, columns = 1, split = 10, num_perms = 50000)
  
  p_list[[i]] <- result_set %>% 
    as.data.frame()%>%
    mutate_if(is.numeric, function(x) p.adjust(p = x, method = "BH")) 
}
p_list %>% 
  lapply(., function(x) mutate(x, voxel = 1:400)) %>%
  bind_rows() %>%
  as.data.frame() %>%
  mutate(effect_size = rep(effect_size[1:8], each=400),
         voxel = factor(voxel)) %>%
  dplyr::filter(voxel %in% c(134, 135, 144, 145, 234, 235, 244, 245) | V1 <= 0.05) %>%
  mutate(real_diff = ifelse(voxel %in% c(134, 135, 144, 145, 234, 235, 244, 245), "real", "FP")) %>%
  ggplot(aes(x = effect_size, y = V1, col = voxel, group = voxel)) + 
  geom_line(aes(linetype = real_diff))+
  ylab("P-Value") +
  xlab("Effect Size")+
  ggtitle("Fixed Sample Size of 30 per subgroup")
```

#Changing Sample Sizes
```{r, echo = FALSE}
#things to append/use iteratively
sample_size <- seq(30,80,5)
p_list2 <- vector("list")

#fixed things
img.dim <- c(10,10,4)


for(i in 1:length(sample_size)){
  n <- sample_size[i]*4
  sub_n <- sample_size[i]
  set.seed(i)
  voxel_data <- array(rnorm(prod(img.dim)*n),dim=c(img.dim,n))
  cov_mat_parperm <- cbind(rep(c(0,1),c(sub_n*2,sub_n*2)), rep(c(0,1,0,1),rep(sub_n,4)))
  xtx <- xmat_trans(cov_mat_parperm[(n/2 + 1):n,-1])
  voxel_data_set_i <- voxel_data
  voxel_data_set_i[4:5, 4:5, 2:3, (n-sub_n + 1):n] <- voxel_data_set_i[4:5, 4:5, 2:3, (n-sub_n + 1):n] + 1.0
  simulation_nifti <- nifti(voxel_data_set_i, dim = c(10, 10, 4, n))
  ymat_set <- ymat_trans(simulation_nifti)[,(n/2 + 1):n]
  
  
  cores <- detectCores()
  cl <- makeCluster(cores[1]-1)
  registerDoParallel(cl)
  
  result_set <- run_permtest(x.mat = xtx, y = ymat_set, columns = 1, split = 2, num_perms = 20000)
  
  p_list2[[i]] <- result_set %>% 
     as.data.frame()%>%
     mutate_if(is.numeric, function(x) p.adjust(p = x, method = "BH")) 
}

p_list2 %>% 
  lapply(., function(x) mutate(x, voxel = 1:400)) %>%
  bind_rows() %>%
  as.data.frame() %>%
  mutate(sample_size = rep(sample_size, each=400),
         voxel = factor(voxel)) %>%
  dplyr::filter(voxel %in% c(134, 135, 144, 145, 234, 235, 244, 245) | V1 <= 0.05) %>%
  mutate(real_diff = ifelse(voxel %in% c(134, 135, 144, 145, 234, 235, 244, 245), "real", "FP")) %>%
  ggplot(aes(x = sample_size, y = V1, col = voxel, group = voxel)) + 
  geom_line(aes(linetype = real_diff)) + 
  ylab("P-Value") +
  xlab("Sample Size")+
  ggtitle("Fixed Effect Size of 1.0")
```