---
title: "parPerm for interaction effects"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Interaction effects using permutation testing}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#Simulation 2:
 - Three-group permutation test
 - n=120 (40 per group)
 - Number of voxels: 10 x 10 x 4
 - Significant area size: 2 x 2 x 1
 - Multiple comparison correction (p.adjust, method=BH)
 - Report false discovery rates. 
 - Factor 1: txt, Factor2: sex
 - Only interaction size of d=0.8
(e.g. generate 4 groups, 30 per groups, and only one group will have higher average)


```{r, include = FALSE}
library(tidyverse)
library(parPerm)
library(doParallel)
library(knitr)
library(oro.nifti)
```

```{r Create Dataset}
img.dim <- c(10,10,4)
n <- 120
set.seed(1)
voxel_data <- array(rnorm(prod(img.dim)*n),dim=c(img.dim,n))

#Create dataset with effect size (0, 0, 0.8)
voxel_data_set1 <- voxel_data
voxel_data_set1[4:5,4:5,3,91:120] <- voxel_data_set1[4:5,4:5,3,91:120] + 1.3

#Show the means have actually changed
lapply(1:90, function(x) mean(voxel_data_set1[4:5,4:5,3,x])) %>% unlist() %>% mean
lapply(91:120, function(x) mean(voxel_data_set1[4:5,4:5,3,x])) %>% unlist() %>% mean

#Create the nifti file
simulation_nifti <- nifti(voxel_data_set1, dim = c(10, 10, 4, 120))
#writeNIfTI(simulation_nifti, "simulation2_data")
```

```{r}
cov_mat_parperm <- cbind(rep(c(0,1),c(60,60)), rep(c(0,1,0,1),c(30,30,30,30)))

#Set1 -- where first column x = 0
xtx_1 <- xmat_trans(cov_mat_parperm[1:60,-1])
ymat_set1 <- ymat_trans(simulation_nifti)[,1:60]
cores <- detectCores()
cl <- makeCluster(cores[1]-1)
registerDoParallel(cl)

#miswrote the single column version
result_set1 <- run_permtest(x.mat = xtx_1, y = ymat_set1, columns = 1, split = 2, num_perms = 10000)

result_set1 %>% 
  as.data.frame()%>%
  mutate_if(is.numeric, function(x) p.adjust(p = x, method = "BH")) %>%
  arrange(V1) %>%
  head() %>% 
  kable()
```

```{r}
#Set2 -- where first column x = 1
xtx_2 <- xmat_trans(cov_mat_parperm[61:120,-1])
ymat_set2 <- ymat_trans(simulation_nifti)[,61:120]
cores <- detectCores()
cl <- makeCluster(cores[1]-1)
registerDoParallel(cl)

#miswrote the single column version
result_set2 <- run_permtest(x.mat = xtx_2, y = ymat_set2, columns = 1, split = 2, num_perms = 10000)

result_set2 %>% 
  as.data.frame()%>%
  mutate_if(is.numeric, function(x) p.adjust(p = x, method = "BH")) %>%
  arrange(V1) %>%
  head() %>% 
  kable()
```

Even parsing it out, doesn't quite seem to isolate the effect when effect size is 0.8. 

Suggesting if we up the effect size it might parse it out. Using 1.3 it starts to show. 