---
title: "Comparing mclapply vs foreach"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{comparing_methods}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
```{r, echo = FALSE, message = FALSE, warning = FALSE}
#load libraries
library(parallel)
library(tidyverse)
library(readxl)
library(oro.nifti)
library(doParallel)
library(foreach)
library(knitr)
library(parPerm)
```

###Cleanup our outcome data
```{r, warning = FALSE, message = FALSE}
gmvol<-readNIfTI('../../../neuroimaging/4d6mmnew.nii.gz')
mask<-readNIfTI('../../../neuroimaging/vol0000.nii.gz')
ymat <- ymat_trans_mask(neurodat = gmvol, mask = mask)
```

###Cleanup our predictor variables
```{r, warning = FALSE, message = FALSE}
xmat <- data.frame(read_excel('../../../neuroimaging/VMB Variables.xlsx',skip=1))
xtx <- xmat_trans(xmat)
```

###Comparing Permutation test between mclapply vs foreach
```{r, warning = FALSE, message = FALSE}
permtest.oneunit<-function(xmat=xtx,y=ymat,seed=1234){
  set.seed(seed)
  n=nrow(xtx)
  indx=sample(n,n,replace=FALSE)
  bhat<- y %*% xmat[indx, 2:3] #####-----why only second and third column (groups), test the beta coefficient of the groups
  return(bhat)
}

run_pertest<-function(x.mat=xtx,y=ymat){
  
  vindx=rep(1:101,each=floor(nrow(ymat)/100))[1:nrow(ymat)]
  
  bhat = y %*% x.mat[,2:3]
  
  rr1=lapply(1:101, function(k){
    perms<-mclapply(1:100,function(seednum){permtest.oneunit(xmat=xtx,seed=seednum,y=y[vindx ==k,])},mc.cores=8)
    aa1=do.call(rbind,lapply(perms,function(x)x[,1]))
    ps1=apply(rbind(bhat[vindx==k,1],aa1),2, function(x)sum( x[-1]> abs(x[1]) |  x[-1]< (-1*abs(x[1])) ))/100
    
    aa2=do.call(rbind,lapply(perms,function(x)x[,2]))
    ps2=apply(rbind(bhat[vindx==k,2],aa2),2, function(x)sum( x[-1]> abs(x[1]) |  x[-1]< (-1*abs(x[1])) ))/100
 
    return(cbind(unlist(ps1),unlist(ps2)))})
  
  return(do.call(rbind,rr1))
}
```

###Runtime using mclapply
```{r}
system.time(run1 <- run_pertest(x.mat=xtx,y=ymat))
```

###Runtime using foreach
```{r}
cl <- makeCluster(8)
registerDoParallel(cl)
system.time(run2 <- run_permtest_multicat(x.mat = xtx, y = ymat, columns = 2:3, split = 101, num_perms = 100))
```

###Verifying same results
```{r}
print(cbind(head(run1), head(run2)))
```

As we can see, by utilizing a foreach structure, built into the run_permtest_culticat function from this package, rather than that of one that relies on mclapply, we have cut around 20% of runtime for permutation test calculations. Performance may vary depending on operating system (this was done on macOS). 